Exoplanet population inference and the rate of Earth analogs \\ from noisy, incomplete catalogs

### 2014-06-09 document/ms.tex

>>>>

We have developed a hierarchical probabilistic framework for inferring the
population of exoplanets based on noisy incomplete catalogs.
This method incorporates systematic treatment of observational uncertainties
and detection efficiency.
One major benefit of this framework is that it provides the best possible
constraints on the population under the stated assumptions.
After demonstrating the validity of our method on two qualitatively different
synthetic exoplanet catalogs, we run our inference on a published catalog of
small exoplanet candidates orbiting Sun-like stars (\citealt{petigura}) to
determine the occurrence rate density of exoplanets as a function of period
and radius.
We extrapolate this measurement to the location of Earth and constrain the
rate density of Earth analogs with large error bars.
